NSHRDLU:\thanks{Name is provisional, and stolen from Geoff Hinton.}\\Work in progress on the joint learning of parsing and semantic encoding

### 2016-01-19 writing/gist/gist.tex
Gist update.

\newcommand\todo[1]{\textcolor{blue}{\textbf{TODO:} #1}}

@@

@@

@@

The composition function in the basic model (green) combines only the top elements of the stack, without using any further information. It may be possible to encourage the composition function to learn to do some amount of context-sensitive interpretation/disambiguation by adding a connection from the tracking LSTM (red) directly into the composition function.

For Model 0, no tracking LSTM is needed for the ordinary operation of the model, but it would be possible to add one for this purpose, taking as inputs the top two values of the stack at each time point and emitting as output a context vector that can be used to condition the composition function.

@@

@@

\todo{JG, fill out.}

@@

@@

>>>>

\newcommand\todo[1]{\textcolor{red}{\textbf{TODO:} #1}}
\newcommand\note[1]{\textcolor{blue}{\textbf{NOTE:} #1}}

@@

\subsection{Publication plans}

\subsubsection{Winter 2016}

@@

\subsubsection{Spring 2015}

Our second paper will be focused on the soft stack models, Models 3 and 4. It will investigate the role of differentiable stack data structures in sentence encoding and the possibility of learning consistent and useful syntactic parsers using only semantic supervision.

@@

The composition function in the basic model (green) combines only the top elements of the stack, without using any further information. We can encourage the composition function to learn to do some amount of context-sensitive interpretation/disambiguation by adding a connection from the tracking LSTM (red) directly into the composition function.

For Model 0, no tracking LSTM is needed for the ordinary operation of the model, but we can simply add one for this purpose, taking as inputs the top two values of the stack at each time point and emitting as output a context vector that can be used to condition the composition function.

So far, we have found this technique to yield non-trivial performance gain. A clearer evaluation on converged models is forthcoming.

@@

\todo{[AR, RG] Write up the attention equations that you use.}

\todo{[Anyone -- Sam can] Draw a diagram indicating the structure of constituent by constituent attention.}

\note{Not currently planned.}

\note{Not currently planned.}

@@

\todo{[JG] Explain.}

@@

\todo{Does anyone know of a better baseline TreeRNN implementation that we can use on Jagupard? We can use the CoreNLP SST model, but using a Java model as a baseline seems worrying unless we're guaranteed that it's competitively fast.}

@@

\note{We're running sentiment experiments to evaluate the behavior of converged models, since SNLI takes too long to train to convergence. However, we don't currently plan to publish SNLI results.}
